---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Clothing Brand and Style Preferences Report

This dynamic report explores trends and preferences in clothing brands, styles, and user ratings based on self-logged survey data.

The dataset includes responses with time stamps, preferred clothing brands, ratings (on a scale), style descriptors, and optional comments. This analysis helps us understand which brands are most popular, how users rate their outfits, and how styles are distributed.

We analyse a total of `r nrow(latest_data)` logged entries.  
The average rating across all responses is `r round(mean(latest_data$rating), 2)`, with the highest rating being `r max(latest_data$rating)` and the lowest `r min(latest_data$rating)`.


```{r}
# Loading tidyverse package
library(tidyverse)

# Reading the published CSV file into the data frame
csv_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vQBcXpQL2dO9NrRDs1qhCm0ZRaOiotvDzKJYXxynh0JwBucUliUm2B-hoGpuUG1vS7vPA8Yl9nArLJu/pub?gid=192450215&single=true&output=csv"
logged_data <- read_csv(csv_url)

# Renaming the variabes in the data frame
latest_data <- logged_data %>%
  rename(timestamp = 1,
         time = 2,
         brand = 3,
         rating = 4,
         style = 5,
         comment = 6)

# Check structure of data
glimpse(latest_data)

# Number of entries (rows)
num_entries <- nrow(latest_data)

# Mean rating
mean_rating <- mean(latest_data$rating, na.rm = TRUE) %>% round(2)

# Maximum rating
max_rating <- max(latest_data$rating, na.rm = TRUE)

# Minimum rating
min_rating <- min(latest_data$rating, na.rm = TRUE)
```

### Summary Stats

- Total number of entries: `r num_entries`
- Mean rating (by me): `r mean_rating`
- Highest rating: `r max_rating`
- Lowest rating: `r min_rating`

These figures summarise how people scored according to my personal fashion ratings. A mean rating of `r mean_rating` shows the general quality of outfits I’ve come across — pretty solid overall!

